\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-11-01 demystify.tex
updates

\begin{document}
\maketitle

@@

@@

\begin{wrapfigure}{r}{0.47\linewidth}
\vspace{-0.2in}
      \begin{center}
        \includegraphics[width=1\linewidth]{c6.png}
      \end{center}
      \vspace{-0.1in}
\end{wrapfigure}
Many students have letters written by themselves and signed by their professors. These have little
values. We can recognize them and will consider them weakness.
Similarly, many professors write generic letters for students, e.g., the students didn't do any
research or make any impression for the professor to write about. These letters are also not useful and considered weak.

Many students get letters from supervisors from company where they did internship or are
working at. It is OK as long as it is a research-based personalized
letter (once again, we are talking about PhD applications, not MS).

>>>>

\begin{document}
\setcounter{section}{-1};

\maketitle

@@

\section{Summary}\label{sec:summary}
Here we summarize the main points of the document. This allows you to quickly skim through the document and decide which parts you want to read in detail.
\begin{enumerate}
\item Should you apply?
\begin{itemize}
    \item Yes, definitely.  CS PhD study in the US is fully funded and admission into good universities is not any harder than non-US schools.
\end{itemize}
\item How is your application evaluated?
\begin{itemize}
    \item Applications are evaluated by a committee and each application is reviewed by typically 3 faculty.
    \item Individually faculty cannot directly admit a student (so do not email and ask if you have a chance), but they can \emph{advocate} for a student (so do email and introduce yourself if you share the same research interest).
    \item The committee will look at various factors, but the most important ones are research ability, e.g., publications, and recommendation letters.
    \item LORs are important, but only if they are personalized and talk about your research ability.
    \item GRE \emph{is not} required by most schools.
    \item Grades are important, but only if your school is well-known. Otherwise, they are not useful.
\end{itemize}
\end{enumerate}

\begin{itemize}
    \item 
\end{itemize}

@@

\begin{center}
\includegraphics[width=0.6\linewidth]{c6.png}
\end{center}

Many students have letters written by themselves and signed by their professors. These have little
values. We can recognize them and will consider them weakness.
Similarly, many professors write generic letters for students, e.g., the students didn't do any
research or make any impression for the professor to write about. These letters are also not useful and considered weak.

Many students get letters from supervisors from companies where they did internships or are working at. It is OK as long as it is a research-based personalized letter (once again, we are talking about PhD applications, not MS).
